Tor's Usability for Censorship Circumvention

### 2015-10-05 paper/circumvention-experiment.tex
Fix more style issues

\begin{itemize} \itemsep1pt \parskip0pt \parsep0pt
\item {\bfseries Mild censorship} 
(Reflective of countries such as {\color{red}?? and ??}.)
Certain domain names are blocked. Reaching these 
domains requires any use of a censorship circumvention 
tool. The default option to ``connect'' to the Tor network 
directly will circumvent this censor. Additional correct
bridge or proxy configuration are optional. 
\item {\bfseries Intermediate censorship} 
(Reflective of countries such as {\color{red}?? and ??}.)
Certain domain names are blocked. Censorship circumvention
tools are blocked. Since Tor is blocked by blocking all public Tor
relay nodes, the default option to ``connect'' to the Tor network
directly will fail. A choice of a hard-coded bridge (see Figure ~\ref{fig:bridges})
or a valid non-public bridge is required to circumvent this censor.  
Additional correct proxy configuration is optional.
\item {\bfseries Comprehensive censorship} 
(Reflective of countries such as China and Syria.)
Certain domain names are blocked. Censorship circumvention tools
are thoroughly blocked. Tor is blocked by blocking all public
Tor relay nodes, and the censor has examined source code to block
all hard-coded bridge relays in the configuration interface. The default option
to ``connect'' to the Tor network directly will fail. Choosing any other bridges than
``meek-amazon,'' ``meek-azure,'' and``meek-google,'' will fail. This is because 
domain-fronting requires censors to block entire CDNs to also block this
transport (which will cause huge collateral blocking damage), making it resistant to agressive censorship environments. Additional details,
see ~\cite{fifield2015blocking}.\\
\end{itemize}

\noindent {\bfseries List of Tasks} 
In our experimental setup, successful completion of 
these given tasks requires of correct configuration.
The difficulty of circumventing  censorship to visit the 
websites required for the tasks will vary on the 
simulated censorship environment. Since all participants will be given the 
same set of tasks, regardless of the censorship environment, 
the difficulty of completing the tasks remains constant assuming
correct configuration. The tasks themselves are not intended to
be challenging.

@@

\begin{itemize} \itemsep1pt \parskip0pt \parsep0pt
\item {\bfseries Test the Tor configuration interface} We will perform the largest-scale user study 
of Tor to date, measuring how users configure Tor in three different adversarial settings. 
\item {\bfseries Test an improved configuration interface} With the measurements collected
from testing the interface as-is, Nathan will be designing ways to improve the interface to minimize
time taken, paths taken, and error states reached.
\item {\bfseries Test an alternative configuration interface} A Tor developer has offered
to design a mock-up interface for an alternative configuration interface which will
greatly automate the process. There are tradeoffs between ease of use and transparency
of the system's, and ethical considerations with loggable errors resulting from automated configuration. 
\item {\bfseries Push changes} We have the support of Tor developers
to improve this interface. Additionally, since the configuration interface does not require 
any changes to the Tor Browser functionality, improvements to the interface will
be easy to deploy. 
\end{itemize}

>>>>

\begin{itemize} \itemsep1pt \parskip0pt \parsep0pt
\item {\bfseries Mild censorship} 
(Reflective of countries such as {\color{red}?? and ??}.)
Certain domain names are blocked. Reaching these 
domains requires any use of a censorship circumvention 
tool. The default option to ``connect'' to the Tor network 
directly will circumvent this censor. Additional correct
bridge or proxy configuration are optional. 
\item {\bfseries Intermediate censorship} 
(Reflective of countries such as {\color{red}?? and ??}.)
Certain domain names are blocked. Censorship circumvention
tools are blocked. Since Tor is blocked by blocking all public Tor
relay nodes, the default option to ``connect'' to the Tor network
directly will fail. A choice of a hard-coded bridge (see Figure ~\ref{fig:bridges})
or a valid non-public bridge is required to circumvent this censor.  
Additional correct proxy configuration is optional.
\item {\bfseries Comprehensive censorship} 
(Reflective of countries such as China and Syria.)
Certain domain names are blocked. Censorship circumvention tools
are thoroughly blocked. Tor is blocked by blocking all public
Tor relay nodes, and the censor has examined source code to block
all hard-coded bridge relays in the configuration interface. The default option
to ``connect'' to the Tor network directly will fail. Choosing any bridges other than
``meek-amazon,'' ``meek-azure,'' and``meek-google,'' will fail. This is because 
domain-fronting requires censors to block entire CDNs to also block this
transport (which will cause huge collateral blocking damage), making it resistant to agressive censorship environments.
(See ~\cite{fifield2015blocking} for additional details.)\\
\end{itemize}

\noindent {\bfseries List of Tasks} 
In our experimental setup, successful completion of 
these given tasks requires of correct configuration.
The difficulty of circumventing  censorship to visit the 
websites required for the tasks will vary depending on the 
simulated censorship environment. Since all participants will be given the 
same set of tasks, regardless of the censorship environment, 
the difficulty of completing the tasks remains constant assuming
correct configuration. The tasks themselves are not intended to
be challenging.

@@

\begin{itemize} \itemsep1pt \parskip0pt \parsep0pt
\item {\bfseries Test the Tor configuration interface} We will perform the largest-scale user study 
of Tor to date, measuring how users configure Tor in three different adversarial settings. 
\item {\bfseries Test an improved configuration interface} With the measurements collected
from testing the interface as-is, we will be designing ways to improve the interface to minimize
time taken, paths taken, and error states reached.
\item {\bfseries Test an alternative configuration interface} A Tor developer has offered
to design a mock-up interface for an alternative configuration interface which will
greatly automate the process. There are tradeoffs between ease of use and transparency
of the systems, and ethical considerations with loggable errors resulting from automated configuration. 
\item {\bfseries Push changes} We have the support of Tor developers
to improve this interface. Additionally, since the configuration interface does not require 
any changes to the Tor Browser functionality, improvements to the interface will
be easy to deploy. 
\end{itemize}
